Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed the awkward space between the x-axis and main plot

publications_per_year_plot <- ggplot(data = publications_per_year) +
  geom_bar(aes(x = publication_year,
               y = n
               ),
           stat = 'identity',
           color = 'black',
           fill = 'tomato3'
           ) +
  scale_y_continuous(breaks = seq(0, 30, 2),
                     labels = seq(0, 30, 2)
                     ) +
  labs(x = "Year of publication", y = "Number of papers") +
  theme_minimal(base_size = 12)

>>>>

publications_per_year_plot <- ggplot(data = publications_per_year) +
  geom_bar(aes(x = publication_year,
               y = n
               ),
           stat = 'identity',
           color = 'black',
           fill = 'tomato3'
           ) +
  scale_y_continuous(breaks = seq(0, 30, 2),
                     labels = seq(0, 30, 2),
                     expand = c(0, 0)
                     ) +
    scale_x_continuous(breaks = seq(1970, 2020, 5),
                     labels = seq(1970, 2020, 5)
                     ) +
  labs(x = "Year of publication", y = "Number of papers") +
  theme_minimal(base_size = 12)
